### 2014-03-12 src/methodology.Rnw
udpate

\subsubsection{x\% selection over program elements (and variations)}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection criteria to sample from within different program
elements.  We sampled in the increasing order of scope,
--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
scope was analyzed as part of x\% selection).

>>>>

\subsubsection{Sampling over program elements (and variations)}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection criteria to sample from within different program
elements.  We sampled in the increasing order of scope,
--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
scope was analyzed as part of x\% selection).
